\textbf{Volatility and the Buyback Anomaly}

### 2016-05-03 manuscriptJF.Rnw
minor

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
#dev.off();
#library(knitr); knit2pdf('bb_issuers.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists

#load("tmpfiles/bb_issuersALL.Rdata")
reload_data = 0

# Then to make it into Word: 
# pandoc -s bb_issuers.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx

generate_all_data = 0 # set this to 1 if the data need to be re-generated from the csv's even though they already exist as .Rdata. 
# TIME ALIGNMENT IS KEY, SO WE HAVE A SEPARATE PART OF THE CODE FOR THIS
time_align_all_data = 0
# Some basic data generation that we need across events
rerun_buyback_data_code <- 0
rerun_issuers_data_code <- 0
# If we generate the cross-events data again
get_crossevent_data <- 0 # Old stuff, not used for now
# report_code is only customized to change the "high U-index" and "low U-index" companies, nothing else. Everything else is done in report_data.R
rerun_buyback_report_code <- 0
rerun_issuers_report_code <- 0
# All the RNW data
generate_rnw_data = 0

source("lib_helpers.R")
source("latex_code.R")
source("dataset/indices_and_factors/ff_industries_sic.R")
source("business_data_clean.R")
source("Paper_global_parameters.R")

if (generate_rnw_data == 1){
  source("bb_issuers.R")
}  else{
  if (reload_data)
    load("tmpfiles/bb_issuersALL.Rdata")
  source("lib_helpers.R") 
  source("latex_code.R")
  source("dataset/indices_and_factors/ff_industries_sic.R")
  source("business_data_clean.R")
  source("Paper_global_parameters.R")
}

@@

# use comma for 1000s
knit_hooks$set(inline = function(x) {
  if(is.numeric(x)){
    return(prettyNum(x, big.mark=","))
  }else{
    return(x)
  }
})

@@

% Notes options
\ifnotes{%
\usepackage[margin=1in,paperwidth=10in,right=2.5in]{geometry}%
\usepackage[textwidth=1.4in,shadow,colorinlistoftodos]{todonotes}%
}{%
\usepackage[margin=1in]{geometry}%
\usepackage[disable]{todonotes}%
}

@@

% JFE-specific includes:

\usepackage{indentfirst} % Indent first sentence of a new section.
\usepackage{jfe}          % JFE-specific formatting of sections, etc.
\usepackage[labelfont=bf]{caption} % bold captions

@@

\setlist{noitemsep}  % Reduce space between list items (itemize, enumerate, etc.)
%\onehalfspacing      % Use 1.5 spacing
% Use endnotes instead of footnotes - redefine \footnote command

\title{Share Buyback and Equity Issue Anomalies Revisited}%\footnotetext{}

\author{Theodoros Evgeniou$^*$, Enric Junqu\'e de Fortuny$^*$,\\
Nick Nassuphis$^{**}$, and Theo Vermaelen\thanks{INSEAD, Bd de Constance, 77300 Fontainebleau, France, phone: +33(0)1 6072 4000, $^{**}$31, St. Martin's Lane WC2N 4ER London, United Kingdom, e-mail:   \href{mailto:theodoros.evgeniou@insead.edu}{theodoros.evgeniou@insead.edu}, \href{mailto:enric.junquedefortuny@insead.edu}{enric.junquedefortuny@insead.edu},  \href{mailto:nicknassuphis@gmail.com}{nicknassuphis@gmail.com}, and \href{mailto:theo.vermaelen@insead.edu}{theo.vermaelen@insead.edu}. }}

@@

\vspace{-.2in}
\begin{abstract}
\noindent We re-examine the behavior of stock returns after net issue announcements using the five-factor model proposed by Fama and French (2015a). We confirm their findings that the equity issue anomaly disappears with the five-factor model, but the buyback anomaly does not. Buyback announcements by firms with high pre-announcement (idiosyncratic) volatility are followed by higher long-term abnormal returns. This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.

\end{abstract}
\vspace{2cm}

@@

\noindent  \textit{JEL classification}: G35; G14; G32

\medskip
\noindent \textit{Keywords}: Share Buybacks; Seasoned Equity Offerings; Anomalies

@@

The fact that companies experience long-term positive excess returns after share buybacks and negative long term excess returns after equity issues, has been documented extensively in the academic literature.\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}. For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}  In spite of these well documented anomalies investors are not less excited today about e.g., a buyback announcement than 30 years ago: on average stock prices increase by approximately 2 to 3$\%$  when companies announce that the board of directors has approved a buyback program. Moreover, we find very few funds that specialize in exploiting these anomalies.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA. The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization. We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} The fact that these anomalies have not generated a significant response from investors and asset management firms is somewhat surprising considering that other anomalies have disappeared after being documented in academic research~\citep{McLean2016}. What makes these capital structure anomalies different so that they stand the test of time?

One straightforward explanation is that they are not really anomalous returns but compensation for risk. Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the \cite{Carhart1997} 4-factor model as benchmarks. However, \cite{FamaFrench2015b}  argue that the buyback and equity issue anomalies do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns. This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}. If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research. Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies. First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}. For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization \citep{StephensWeisbach1998}. Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues). The part of their sample where net equity issues are positive is defined as the ``buyback sample''. But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations. Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares. However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors. In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only affects selling shareholders who leave the firm. In this paper we re-examine the anomaly using the \cite{FamaFrench2015a} model but use announcement dates and separate buyback announcements and equity announcements.

Using buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}, we confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. Even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. An interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive. We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms, and that the anomaly does not disappear if we exclude specific industries. The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.

@@

The results from event studies which use either Ibbotson RATS or the Calendar Time method estimate excess returns and risks contemporaneously. Investors, such as hedge funds, who would like to exploit the anomaly and hedge market risk need however to estimate the factor betas using historical information. If the buyback signals a change in risk \citep{GrullonMichaely2004} hedging market risk may be complicated. That is why in this paper we also simulate hedged investment strategies where we estimate risk before forming the portfolios. We show that an investor who followed such a strategy starting in \Sexpr{firstyear} would by \Sexpr{lastyear} have realized cumulative excess returns between \Sexpr{round(tail(months1,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$, depending on the length of the holding period.

The second major purpose of this paper is to test whether the buyback anomaly is related to the even better known {\it low volatility anomaly}, i.e. (idiosyncratic) volatility is negatively related to expected returns. For example, \cite{Ang2006} find {\it negative} alphas for high volatility and high idiosyncratic volatility stocks, using the 3-factor \cite{FamaFrench1993} model. Moreover, \cite{FamaFrench2015b} show that, using the 5-factor model, this anomaly persists for small firms. However, in our buyback sample we find a significant {\it positive} relation between excess returns, using the Fama-French 5-factor model as a benchmark. This is consistent with the {\it information advantage hypothesis}: in firms with high idiosyncratic risk volatility is largely driven by company-specific information, and for such firms it is more likely that management is better informed than the market. The result is also consistent with the  {\it costly arbitrage hypothesis} of \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued  stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.}  Their argument is that idiosyncratic volatility represents arbitrage risk and deters arbitrage and the resulting reduction in mispricing.  So, among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced.

Turning to total volatility we also find that buyback authorizations of high risk stocks are followed by larger excess returns. This is consistent with the {\it option hypothesis}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks \citep{IkenberryVermaelen1996}. If markets underestimate the value of this option at the time of the buyback authorization, excess returns should be positively correlated with volatility.

Combining idiosyncratic risk and total volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index, improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high Enhanced Undervaluation Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

This paper is organized as follows. In section 2 we describe our data. In section 3 we test whether buyback and equity issue anomalies survive when we use the \cite{FamaFrench2015a} five-factor model. We also compare firms that buy back stock and issue equity within 48 months of a buyback announcement with firms that do not issue stock subsequently. In section 4 we test whether the buyback anomaly is robust across time, investment horizon and industry. In section 5 we test whether idiosyncratic risk as well as volatility can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}. Section 6 concludes.

@@

Our sample spans the period from January \Sexpr{firstyear} to December \Sexpr{lastyear}. We start in \Sexpr{firstyear} as SDC's coverage is poor before that year. We stop in \Sexpr{lastyear}, the last year all CRSP and Compustat data were available. We retrieved buyback authorization announcements and announcements of Secondary Equity Offerings (SEO's) from the Securities Data Corporation (SDC) database. Daily and monthly returns, pre-announcement daily closing prices and market capitalization data were taken from CRSP. Book value of equity (BE) was taken from Compustat. The Fama-French factors and breakpoints were obtained from Kenneth French's website.

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request. An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. The average percent of shares authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).

>>>>

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#dev.off();
#library(knitr); knit2pdf('manuscriptJF.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscriptJF",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists
# Then to make it into Word: 
# system("pandoc -s manuscriptJF.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")

rm(list=ls()) # Clean up the memory, if we want to rerun from scratch

generate_all_data = 0 # set this to 1 if the data need to be re-generated from scratch
generate_rnw_data = 0 # set this to 1 to generate the .Rnw data

if (generate_all_data == 1){
  source("create_bbissuers_data.R")
}
if (generate_rnw_data == 1){
  source("bb_issuers_new.R")
} else {
  load("bb_issuers_new.Rdata")
}

source("../FinanceLibraries/lib_helpers.R", chdir=TRUE)
source("../FinanceLibraries/latex_code.R")
source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
source("Paper_global_parameters.R")

@@

if (0){ # To add later
  qfactors <- read.csv("dataset/indices_and_factors/qfactors.csv", sep=";", dec=".")
  rownames(qfactors) <- paste(qfactors[,1],ifelse(str_length(qfactors[,2]) == 2, qfactors[,2], paste("0",qfactors[,2], sep="")), sep="-")
  useonly = which(rownames(qfactors) %in% str_sub(rownames(Risk_Factors_Monthly), start = 1, end=7))
  qfactors = qfactors[useonly,]
  rownames(qfactors) <- rownames(Risk_Factors_Monthly)[match(rownames(qfactors), str_sub(rownames(Risk_Factors_Monthly), start = 1, end=7))]
  qfactors = qfactors[,3:6]
  qfactors = apply(qfactors,2,function(r) as.numeric(str_replace(r,",",".")))
  qfactors = qfactors/100
  qfactors = cbind(qfactors,Risk_Factors_Monthly[,c("SMB", "HML","RF","RMW","CMA")])
  formula_used="(ri - RF) ~ MKT + HML + ME + I.A + ROE"
  qfactors_irats_MKT_HML_ME_IA_ROE = car_table(BUYBACK_DATA$DATASET$returns_by_event_monthly, BUYBACK_DATA$DATASET$SDC$Event.Date, qfactors, formula_used = formula_used)$results
  qfactors_irats_MKT_HML_ME_IA_ROE = qfactors_irats_MKT_HML_ME_IA_ROE[reported_times,]

}

inline_hook <- function (x) {
  if (is.numeric(x)) {
    # ifelse does a vectorized comparison
    # If integer, print without decimal; otherwise print two places
    res <- ifelse(x == round(x),
                  # use comma for 1000s
                  sprintf("%s", prettyNum(x, big.mark=",")),
                  sprintf("%.2f", x)
    )
    paste(res, collapse = ", ")
  } else {
    x
  }
}
knit_hooks$set(inline = inline_hook)
@

@@

\usepackage[margin=1in,top=1.5in,bottom=1.5in]{geometry}%
\usepackage[disable]{todonotes}%
%\linespread{1.3}
\onehalfspacing      % Use 1.5 spacing

@@

% JF-specific includes:
\usepackage{indentfirst} % Indent first sentence of a new section.
\usepackage{endnotes}    % Use endnotes instead of footnotes
\usepackage{jf}          % JF-specific formatting of sections, etc.
\usepackage[labelfont=bf,labelsep=period,justification=centering]{caption}   % Format figure captions
\captionsetup[table]{labelsep=newline,labelfont=bf,textfont=bf}
\captionsetup[figure]{labelfont=bf,justification=justified}
\pagestyle{myheadings}

@@

\setlist{noitemsep}  % Reduce space between list items (itemize, enumerate, etc.)

% Use endnotes instead of footnotes - redefine \footnote command

\title{\textbf{Volatility and the Buyback Anomaly}}%\footnotetext{}

\author{\uppercase{ Theodoros Evgeniou$^*$, Enric Junqu\'e de Fortuny$^{**}$,\\
Nick Nassuphis$^{***}$,} and \uppercase{Theo Vermaelen}\thanks{INSEAD, Bd de Constance, 77300 Fontainebleau, France, phone: +33(0)1 6072 4000, $^{**}$Rotterdam School of Management, Burgemeester Oudlaan 50, 3062 PA Rotterdam, The Netherlands, $^{***}$31, St. Martin's Lane WC2N 4ER London, United Kingdom, e-mail:   \href{mailto:theodoros.evgeniou@insead.edu}{theodoros.evgeniou@insead.edu}, \href{mailto:enric.junquedefortuny@insead.edu}{enric.junquedefortuny@rsm.nl},  \href{mailto:nicknassuphis@gmail.com}{nicknassuphis@gmail.com}, and \href{mailto:theo.vermaelen@insead.edu}{theo.vermaelen@insead.edu}. }}

@@

\vspace{-.2in}
\begin{abstract}
\noindent  We find that, inconsistent with the low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement (idiosyncratic) volatility is high. This is consistent with \cite{Stambaugh2015} who find a positive relation between returns and idiosyncratic volatility for undervalued stocks, and with the prediction that a repurchase authorization is an option for undervalued stocks \citep{IkenberryVermaelen1996}. The buyback anomaly also survives  when using the five-factor model of Fama and French (2015a).  Combining volatility with undervaluation indicators proposed by \cite{PeyerVermaelen2009} improves the predictive power of excess returns after buyback announcements.
\end{abstract}
\vspace{2cm}

@@

%\noindent  \textit{JEL classification}: G35; G14; G32

\medskip
%\noindent \textit{Keywords}: Share Buybacks; Seasoned Equity Offerings; Anomalies; Volatility

@@

The main purpose of this paper is to test whether there is a link between two well-known anomalies: the net issue anomaly, i.e. the fact that share buybacks (equity issues) are followed by long run positive (negative) excess returns\footnote{For evidence on long-term excess returns after buybacks see e.g., \cite{IkenberryLakonishokVermaelen1995,PeyerVermaelen2009,ManconiPeyerVermaelen2015}. For evidence  on under-performance after equity issues see e.g., \cite{LoughranRitter1995,SpiessAffleckGraves1995,Eckboetal2000,DittmarThakor2007,Bravetal2000}.}, and the volatility anomaly, i.e. the fact that (idiosyncratic) volatility is negatively related to expected returns \citep{Ang2006}. This link is plausible considering the fact that \cite{Stambaugh2015} find that the relation between idiosyncratic volatility and future returns reverses and becomes {\it positive} for undervalued stocks.\footnote{They  define undervaluation on the basis of a combination of 11 return anomalies reported in the literature, including net equity issuance.} They argue that their result is consistent with the costly {\it arbitrage hypothesis}: idiosyncratic volatility represents risk that deters arbitrage and the resulting reduction in mispricing, hence among underpriced stocks, the stocks with the highest idiosyncratic volatility should be the most underpriced. As the positive (negative) long run returns after buybacks (equity issues) are generally interpreted as evidence of undervaluation (overvaluation), we would predict also a positive (negative) relation between volatility and future returns after firms announce a buyback (equity issue).

A positive relation between volatility and future returns after buyback authorization announcements is also expected based on the {\it option hypothesis} of \cite{IkenberryVermaelen1996}: a repurchase authorization is an option to take advantage of undervaluation and this option should be more valuable for high volatility stocks. If markets underestimate the value of this option at the time of the buyback authorization, long term excess returns should be positively correlated with volatility. Note that this option hypothesis makes no predictions about excess returns after equity issues which, unlike buyback authorizations, are firm commitments, not options.

In the volatility literature idiosyncratic volatility is estimated by the residual variance of an asset pricing model such as the Fama-French three factor model. Empirically there is a very high correlation between residual variance and total variance (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) so for the remainder of this paper we will use the latter when we refer to just volatility, the volatility anomaly, or the hypotheses above.  We also use an alternative measure of idiosyncratic volatility that is not correlated (\Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$ in this study) with volatility: $1-R^2$. For the remainder of the paper we will use this when we refer to {\it idiosyncratic} volatility. It measures to what extent the volatility of stock returns is explained by company-specific (non-factor related) information [see also \cite{LiRajgopaletal2014}].  The hypothesis that managers are able to time the market [e.g., \cite{IkenberryLakonishokVermaelen1995}] is based on the assumption that managers have superior knowledge about company-specific information. Hence the prediction of the {\it information advantage hypothesis} is that buyback announcements of firms with high idiosyncratic volatility will also generate higher long term excess returns.

Before proceeding with examining the link between anomalies, it is important to verify that these anomalies are real and not simply a proxy for risk, or have disappeared in recent years as has happened with many other ones~\citep{McLean2016}. Excess returns in previous research are calculated using the \cite{FamaFrench1993}  three-factor model or the \cite{Carhart1997} 4-factor model as benchmarks. However, \cite{FamaFrench2015b}  argue that many anomalies are weakened or  do not survive after using the more recent \cite{FamaFrench2015a} five-factor asset pricing model as a model of expected returns. This model incorporates new evidence that profitability and investment patterns, besides market to book and size, explain stock returns \citep{NovyMarx2013}. They find that the volatility anomaly survives for small firms, but the net issue anomaly does not. If buybacks (equity issues) are done by firms with high (low) profitability and few (many) investment opportunities, then these factors may well explain the excess returns reported in previous research. Note, however, that \cite{FamaFrench2015b} do not exactly replicate the papers that first reported the anomalies. First, they assume investors buy after the completion of the buyback and the equity issue, not around the announcement date as e.g., \cite{PeyerVermaelen2009}. For buybacks this may be an issue as repurchases may be completed several years after the buyback authorization \citep{StephensWeisbach1998}. Moreover \cite{FamaFrench2015b} do not examine repurchases and equity issues separately: they calculate returns after net equity issues (funds spent on buybacks minus funds spent on equity issues). The part of their sample where net equity issues are positive is defined as the ``buyback sample''. But this sample still contains some equity issuers, which may introduce a downward bias in the excess returns calculations. Moreover the idea of pooling buybacks and equity issues in ``net issues'' assumes that the decision to issue equity is simply the mirror of buying back shares. However, issuing stock to new investors is not the same as buying back stock from ``old'' selling investors. In the first case, the management has to face new shareholders that may face potential losses, while in the second case the firm only affects selling shareholders who leave the firm. So before concluding that the buyback and equity issue anomalies have disappeared, they have to be examined separately, using announcement dates.

So the second purpose of this paper is to verify whether the buyback and equity issue anomalies still exist using the more recent \cite{FamaFrench2015a} five-factor  model, for buyback and equity announcements during the period \Sexpr{firstyear}-\Sexpr{lastyear}.\footnote{Using throughout this paper the q-factor model of \cite{Houetal2015} instead of the five-factor model of \cite{FamaFrench2015a} leads to the same conclusions.} We confirm the \cite{FamaFrench2015b} conclusion that the five-factor model makes the equity issue anomaly disappear, but the buyback anomaly remains statistically and economically significant. However, even though we find that equity issues are not followed by significant negative excess returns in general, it turns out that using a SEO announcement as a sell signal improves the performance of a buyback portfolio. An interpretation is that firms that are timing the market by buying back shares when they are cheap are also successful timing the market when stocks are expensive. We also confirm that the Undervaluation Index developed by \cite{PeyerVermaelen2009} is a good predictor of excess returns, although it emphasizes smaller firms.
%, and that the anomaly does not disappear if we exclude specific industries. 
The buyback anomaly is also persistent over time and does not seem to become less significant in recent years, which is inconsistent with the hypothesis that the growth of institutional investors and the reduction in trading costs may have made markets more efficient as argued by \cite{FuHuang2015}.

It remains a fact though that the buyback anomaly is to some extent a small firm anomaly, as also found by \cite{PeyerVermaelen2009}: value-weighting all the events (as suggested by~\cite{MitchellStafford2000}) makes the (Calendar Time event study method) alphas disappear, although {\it not} for high volatility stocks as we note below.\footnote{Value weighted Calendar Time method results are available upon request.}  So the anomaly does not challenge the view that 99$\%$ of all stocks may well be priced efficiently. It simply shows that small cap firms are priced less efficiently and managers of these firms are able to take advantage of undervaluation, at least on average. Moreover, while we do not value-weight the events, as argued by \cite{PeyerVermaelen2009}, if anything, to increase the power of the test to detect mispricing, any weighting should be based on the inverse of size. However the negative relation between size and alpha may partly explain why this anomaly persists after 30 years and has attracted very little attention in the asset management industry.\footnote{For example, a Google search for ``buyback funds'' gives very few results: Powershare Buyback Achievers fund, KBC Buyback America, S\&P 500 Buyback ETF, Catalyst/Equity Compass Buyback Strategy fund, and PV Buyback USA. The first 3 funds focus on large caps after buyback completions although the academic research shows abnormal returns are more significant in small, under-priced, value stocks and the relevant event is not the completion of the buyback but the buyback authorization. We are also not aware of event-driven hedge funds that buy repurchasing firms and short equity issuers; typical event-driven strategies are for example based on M\&A arbitrage, capital structure arbitrage or on investing in distressed securities.} Indeed because management fees are proportional to fund size one expects relatively less interest in anomalies concentrated in small caps or microcaps.

@@

After having established that the buyback anomaly survives the Fama-French five factor model and is robust over time, we test for the relation between volatility measures and long term excess returns.  We find a significant {\it  positive} relation between excess returns and volatility as well as idiosyncratic volatility measured by $1-R^2$. 
%Note although there is a high correlation (\Sexpr{100*cor(BUYBACK_DATA$DATASET$CRSP$IVOL,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$) between total volatility and residual variance (the proxy used in the literature for idiosyncratic volatility), the correlation between standardized idiosyncratic volatility and total volatility is only \Sexpr{100*cor(1-BUYBACK_DATA$DATASET$CRSP$Rsq,BUYBACK_DATA$DATASET$CRSP$pre_vol)}$\%$.  
In summary, the positive relation between volatility and excess returns is consistent with the costly arbitrage hypothesis of~\cite{Stambaugh2015} as well as with the option hypothesis of~\cite{IkenberryVermaelen1996}, while the positive relation between $1-R^2$ and excess returns is consistent with the information advantage hypothesis.

Combining  total volatility  and idiosyncratic volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index (EU-Index), improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high EU-Index Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months.

%In order to address the issue of size (which suggests the buyback anomaly is not economically important), we close with a section on buyback anomalies for large firms. We find that there is a buyback anomaly for large firms, but only if we focus on large volatility stocks. This suggests that when there is large uncertainty about fundamental value, even in large firms the option to repurchase stock at prices below fair value is worth a lot. Note however that the alpha for these large high volatility firms is significantly smaller than the alpha of the high EU-Index index so there remains a tradeoff between excess returns and firm size.

This paper is organized as follows. In section 2 we describe our data. In section 3 we test whether the buyback and equity issue anomalies survive when we use the \cite{FamaFrench2015a} five-factor model. We also compare firms that buy back stock and issue equity within 48 months of a buyback announcement with firms that do not issue stock subsequently. In section 4 we test whether the buyback anomaly is robust across time and investment horizon.
%and industry. 
In section 5 we test whether (total) volatility as well as idiosyncratic volatility ($1-R^2$) can improve the predictability of excess returns, relative to simply using the Undervaluation Index proposed by \cite{PeyerVermaelen2009}. Section 6 concludes.

@@

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
cleanup_bb = list()
cleanup_bb$Standardise <- BUYBACK_DATA$cleanupSDC$Standardise
cleanup_bb$biz_clean <- BUYBACK_DATA$cleanupBIZ
cusip_bb = BUYBACK_DATA$DATASET$SDC$CUSIP
event.date_bb = BUYBACK_DATA$DATASET$SDC$Event.Date
permno_bb = BUYBACK_DATA$DATASET$SDC$permno

cleanup_iss = list()
cleanup_iss$Standardise <- ISSUERS_DATA$cleanupSDC$Standardise
cleanup_iss$biz_clean <- ISSUERS_DATA$cleanupBIZ
cusip_iss = ISSUERS_DATA$DATASET$SDC$CUSIP
event.date_iss = ISSUERS_DATA$DATASET$SDC$Event.Date
permno_iss = ISSUERS_DATA$DATASET$SDC$permno
@

Our sample spans the period from January \Sexpr{firstyear} to December \Sexpr{lastyear}. We start in \Sexpr{firstyear} as SDC's coverage is poor before that year. We stop in \Sexpr{lastyear}, the last year all CRSP and Compustat data were available. We retrieved buyback authorization announcements and announcements of Secondary Equity Offerings (SEO's) from the Securities Data Corporation (SDC) database. Daily and monthly returns, pre-announcement daily closing prices and market capitalization data were taken from CRSP. Book value of equity (BE) was taken from Compustat. The Fama-French factors were obtained from Kenneth French's website.

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request. An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, will also be available at \href{http://tevgeniou.github.io/BuybacksIssuers/}{tevgeniou.github.io/BuybacksIssuers.}}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{BUYBACK_DATA$cleanupNoPermno +  BUYBACK_DATA$cleanupNoCRSPdata + BUYBACK_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(BUYBACK_DATA$cleanupBIZ$Industry_filter)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. The average percent of shares authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).
